---
title: "Individual meta-analysis methods"
author: "Darío San-Segundo-Molina, Ignacio Morales-Castilla, Sara Villén-Pérez;"
date: "13/1/2022"
output: html_document
references: references.bib
csl: ecography.csl
bibliography: references.bib
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(brms)
library(nlme)
library(reactable)
```

## Thermal traits pest database:

Thermal traits database (from now on: [*TheTraPest*]{.smallcaps}) have been obtained after several steps:

1.  Literature systematic review
2.  Data preparation: [*Intrapest*]{.smallcaps} database assembly.
3.  Generalized Nonlinear Regression with `nlme::gnls()`
4.  Parameter extraction and *TheTraPest* database assembly.

```{r}
thetrapest <- read_csv("C:/Users/dario-ssm/Documents/Dario Investigacion/IntRaPest/intrinsic_rates_pests/data/parameters_individual_fit_complemented.csv") 
reactable(thetrapest)
```

## Background on meta-analyses and thermal-traits modelling procedures:

#### Statistical models:

We follow considerations of other recent meta-analytical hierarchical models that have been carried out for physiological traits as it is our case [@kharouba2018; @ettinger2020; @buckley2017]. Similarly, except for origin of the data, similar hierarchical models have been used for thermal traits variability [@herrando-pérez2020]; whereas other approaches used more complex analyses such as random forest [@bennett2021].

Accordingly, we will use comparative analyses following different approaches and packages in R [@rcoreteam2021]: *linear mixed-effects* (i.e. *hierarchical*) *regression* with `nlme` package (as in @buckley2017 ?) and alternatively with `metafor` package [@viechtbauer2010].

All models were considered for meta-analysis following existing guidelines in Maximum likelihood [@mengersen2013] (((and Bayesian Inference approaches [@schmid2013]))) on a mixed-effect modelling baseline [@zuur2009a].

#### Meta-analysis features: TO BE DONE SOON

There are different issues that should be taken into account when performing a meta-analysis in ecology: assessment of publication bias and heterogeneity quantification, an appropriate weighting decision and existence of different conditions such as independency between effect size estimators, collinearity among covariates and between-study consistency [@nakagawa2017; @koricheva2014]. Including specific tools such as forest plots, bubble plots, funnel plots and sensitivity analyses to assess and visualize these issues is helpful to detect signal amid noise [@gurevitch2018] and, thus, a recommended (if not mandatory) reliability practice when conducting meta-analysis according to reference manuals )insert ref).

## Analyses: methods

#### Exploratory data analysis

We examine whether outliers should be remove. We select those whose parameter's standard error is lower than Q~95.~ ¿Seguir indicaciones de Harr...?

```{r echo=TRUE}
## apply filters 
range(thetrapest$tmin)
q_tmin <- quantile(thetrapest$tmin, probs = 0.05)
q_tmin_se <-quantile(thetrapest$tmin_se, probs = .95)
range(thetrapest$tmax)
q_tmax <- quantile(thetrapest$tmax,probs = .95)
q_tmax_se <- quantile(thetrapest$tmax_se,probs = .95)
range(thetrapest$topt)
q_topt <- quantile(thetrapest$topt,probs = .95)
q_topt_se <- quantile(thetrapest$topt_se,probs = .95)
ir_dataset_clean_se <- thetrapest %>% 
  filter(tmax_se <= q_tmax_se &
           tmin_se <= q_tmin_se &
           topt_se <= q_topt_se)
reactable(ir_dataset_clean_se)
```

#### Model asssumptions:

Meta-analysis classical methodologies relies on assumptions of normality of the parameter estimates when a non standard effect size metric is used [@handbook2013]. Consequently, we checked normality distribution of the parameters using histograms and Shapiro-tests and using `performance` package to check the model assumptions. These assumptions are not required to be accomplished in the Bayesian approach described below.

1.  **Normality**:

Via histograms, without outliers:

```{r}
#Tmin
lm_tmin <- lm(tmin ~ 1,
              data = ir_dataset_clean_se)
tmin_resid <- lm_tmin$residuals %>% 
  as_tibble()

hist_Tmin_est <- ggplot(tmin_resid, aes(value))+
  geom_histogram(fill = "cadetblue3", binwidth = 1)+
  theme_classic()

#Tmax
lm_tmax <- lm(tmax ~ 1,
              data = ir_dataset_clean_se)
tmax_resid <- lm_tmax$residuals %>% 
  as_tibble()

hist_Tmax_est <- ggplot(tmax_resid, aes(value))+
  geom_histogram(fill = "firebrick2", binwidth = 1)+
  theme_classic()

#Topt
lm_topt <- lm(topt ~ 1,
              data = ir_dataset_clean_se)
topt_resid <- lm_topt$residuals %>% 
  as_tibble()

hist_Topt_est <- ggplot(topt_resid, aes(value))+
  geom_histogram(fill = "purple2", binwidth = 1)+
  theme_classic()
#a
lm_a <- lm(a_est~1,
            data = ir_dataset_clean_se)
a_resid <- lm_a$residuals %>% 
  as_tibble()

hist_a_est <- ggplot(a_resid, aes(value))+
  geom_histogram(fill = "green4", binwidth = 1)+
  theme_classic()

grid_histo <- cowplot::plot_grid(hist_Tmin_est,hist_Tmax_est,hist_Topt_est,nrow = 1)
grid_histo
```

Let's check out the residuals and other assumptions with `performance` .

```{r}
library(performance)
performance::check_model(lm_tmin)
performance::check_model(lm_tmax)
performance::check_model(lm_topt)


# not THAT bad. Some values at some acari...
```

### Summary effects analysis:

For summary effect will be computed after applying a random-effects model with *study* treated as the grouping variable, and each parameterised thermal trait (*i.e.* *T*<sub>min</sub>, *T*<sub>max</sub> and *T*<sub>opt</sub>) as the standardized effect size, following guidelines by @handbook2013. Estimation of the summary effect was computed following \@handbook2013 (see chapter...).

#### a) Tmin

We fitted a random-intercept mixed-effects model to assess lower thermal threshold variability across studies with `lme()`.

```{r}

tmin_intercept <- lme(tmin ~ 1,
                      random = ~1|id,
                      weights = varFixed(~vi),
                      data = ir_dataset_clean_se,
                      control = lmeControl(sigma = 1))
summary(tmin_intercept)
performance::check_model(tmin_intercept)
```

#### Heterogeneity of estimates:

To quantify heterogeneity of the response along categorical or numerical variables, we performed hierarchical linear models (also known as *mixed-effects*) with *study* being treated again as grouping variable and variables of interest as covariates.

-   For **continuous covariates** (i.e. latitude in absolute value), we performed a *meta-regression* (as in @buckley2017 and @deutsch2008 ) with each thermal trait estimate as response variable. Heterogeneity was quantified with *between-studies* explained proportion of variance (*I*<sup>2</sup>) and a new *R*<sup>2</sup> coming from a Q-test [@introduc2009].

-   For **categorical variables**, we performed hierarchical factorial models [@handbook2013] across categorical covariates such as *taxonomic order* and *feeding guild*. In these cases we quantified heterogeneity in a similar way than for covariates, without meta-regression considerations following @introduc2009

In both cases, weights and heterogeneity estimators were computed following reference books [@handbook2013; @introduc2009].

#### Heterogeneity of variation:

Aiming to explore biogeographical hypothesis of *cold-tolerance* $$@bennett2021a; @sunday2019; @herrando-pérez2020$$, we examined how variability of estimates differs among thermal traits. (blablabla) and across latitudes $$@deutsch2008a; @buckley2017$$. Following \@herrando-p?rez2020a, we examined variability using boxplots and tests of variance homogeneity such as Levene's. (interesting if we repeat the batches process by them?).

¿t-test? see possibilities here.

#### Bayesian approach

bla, blablabla, blabla

#### Sensitivity analyses:

bla, blablabla, blab

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
