---
title: "Thermal_traits_metaanalysis_protocol"
author: "Darío San Segundo Molina, Sara Villén Pérez & Ignacio Morales Castilla"
date: "19/1/2022"
output: html_document
bibliography: references.bib
csl: ecography.csl
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(nlme)
library(cowplot)
library(car)
library(brms)
library(knitr)
library(reactable)
library(emmeans)
library(ggthemes)
library(metafor)
```

# Individual-study approach:

## Thermal traits pest database:

Thermal traits database (from now on: [*TheTraPest*]{.smallcaps}) have been obtained after several steps:

1.  Literature systematic review
2.  Data preparation: [*Intrapest*]{.smallcaps} database assembly.
3.  Generalized Nonlinear Regression with `nlme::gnls()`
4.  Parameter extraction and *TheTraPest* database assembly.

```{r, echo = FALSE}
thetrapest <- read_csv("C:/Users/dario-ssm/Documents/Dario Investigacion/IntRaPest/intrinsic_rates_pests/data/thermal_traits_complete.csv") %>% 
  mutate(tol_range = tmax-tmin) %>% 
  mutate(thermal_safety_margin = tmax-topt)
reactable(thetrapest)

```

## Background on meta-analyses and thermal-traits modelling procedures:

#### Statistical models:

We follow considerations of other recent meta-analytical hierarchical models that have been carried out for physiological traits as it is our case [@kharouba2018; @ettinger2020; @buckley2017]. Similarly, except for origin of the data, similar hierarchical models have been used for thermal traits variability [@herrando-pérez2020]; whereas other approaches used more complex analyses such as random forest [@bennett2021].

Accordingly, we will use comparative analyses following different approaches and packages in R [@rcoreteam2021]: *linear mixed-effects* (i.e. *hierarchical*) *regression* with `nlme` package as in @buckley2017 ~~(((((and alternatively with `metafor` package [@viechtbauer2010])))))~~. ~~In addition, to avoid model assumption caveats, we performed a Bayesian hierarchical model as in @kharouba2018 using Stan-compiled `brms` package [@bürkner2017] for R.~~

All models were considered for meta-analysis following existing guidelines in Maximum likelihood [@mengersen2013] and Bayesian Inference approaches [@schmid2013] on a mixed-effect modelling baseline [@zuur2009a].

#### Meta-analysis features:

There are different issues that should be taken into account when performing a meta-analysis in ecology: assessment of publication bias and heterogeneity quantification, an appropriate weighting decision and existence of different conditions such as independency between effect size estimators, collinearity among covariates and between-study consistency [@nakagawa2017; @koricheva2014]. Including specific tools such as forest plots, bubble plots, funnel plots and sensitivity analyses to assess and visualize these issues is helpful to detect signal amid noise [@gurevitch2018] and, thus, a recommended (if not mandatory) reliability practice when conducting meta-analysis according to reference manuals )insert ref).

## Analyses: methods

#### Exploratory data analysis

We examine whether outliers should be remove. We select those whose parameter's standard error is lower than Q~95.~ The dataset that we load here has been already filtered this way, and thermal breadth has also been calculated (see thermal_traits_analysis_sideB.R script)¿Seguir indicaciones de Harr...? Model asssumptions:

Meta-analysis classical methodologies relies on assumptions of normality of the parameter estimates when a non standard effect size metric is used [@handbook2013]. Consequently, we checked normality distribution of the parameters using histograms and Shapiro-tests and using `performance` package to check the model assumptions. These assumptions are not required to be accomplished in the Bayesian approach described below.

1.  **Normality**:

Via histograms, without outliers:

```{r}
#Tmin
lm_tmin <- lm(tmin ~ 1,
              data = thetrapest)
tmin_resid <- lm_tmin$residuals %>% 
  as_tibble()

hist_Tmin_est <- ggplot(tmin_resid, aes(value))+
  geom_histogram(fill = "cadetblue3", binwidth = 1)+
  theme_classic()

#Tmax
lm_tmax <- lm(tmax ~ 1,
              data = thetrapest)
tmax_resid <- lm_tmax$residuals %>% 
  as_tibble()

hist_Tmax_est <- ggplot(tmax_resid, aes(value))+
  geom_histogram(fill = "firebrick2", binwidth = 1)+
  theme_classic()

#Topt
lm_topt <- lm(topt ~ 1,
              data = thetrapest)
topt_resid <- lm_topt$residuals %>% 
  as_tibble()

hist_Topt_est <- ggplot(topt_resid, aes(value))+
  geom_histogram(fill = "purple2", binwidth = 1)+
  theme_classic()
#a
lm_a <- lm(a_est~1,
            data = thetrapest)
a_resid <- lm_a$residuals %>% 
  as_tibble()

grid_histo <- cowplot::plot_grid(hist_Tmin_est,hist_Tmax_est,hist_Topt_est,nrow = 1)
grid_histo
```

## Summary effects analysis:

For summary effect will be computed after applying a **random -intercept** model with *study* treated as the grouping variable, and each parameterised thermal trait (*i.e.* *T*<sub>min</sub>, *T*<sub>max</sub> and *T*<sub>opt</sub>) as the standardized effect size, following guidelines by @handbook2013. Estimation of the summary effect was computed following @handbook2013 (see chapter...).

We fitted a random-intercept mixed-effects model to assess thermal traitsvariability across studies with `lme()`. Note that in a meta-analysis context it is required to weight each study with inverse-variance. Thus, we use the given standard errors (`vi`) and incorporate them at the model with the argument `weights = varFixed(~vi)`. In addition, according to Viechtbauer, **`metafor`** package developer, in nlme package we need to add an argument `control = lmeControl(sigma = 1)` to tell the model that we *indeed* know the variances given at each study (*i.e.* the *sampling variances* representing the *within-studies* variance) and avoid its modelling.

> *"First of all, it's good to see that you are well aware of the fact that lme() without lmeControl(sigma=1) will lead to the estimation of the residual variance component, which implies that the sampling variances specified via varFixed() are only assumed to be known up to a proportionality constant -- however, in the usual meta-analytic models, we assume that the sampling variances are exactly known. In fact, trying to disentangle that residual variance component from any random study effects is usually next to impossible. I mention this explicitly one more time, because I have seen some publications using lme() in exactly this way ..."* -- Viechtbauer ([blog response](https://r-help.stat.math.ethz.narkive.com/ClFcC12h/r-mixed-effects-meta-regression-nlme-vs-metafor)).

And similarly, according to Heisterkamp (2017):

> *For some applications, it is not appropriate to estimate the residual error, especially when it is known in advance based on evidence from past studies, or a theoretically derived scaling parameter. An example of the former are meta-analyses where the standard deviation of individual patient outcomes in each study is reported.*

and Pustejovski (2016) in this [blog post](https://www.jepusto.com/bug-in-nlme-with-fixed-sigma/) :

> *About one year ago, the `nlme` package introduced a feature that allowed the user to specify a fixed value for the residual variance in linear mixed effect models fitted with `lme()`. This feature is interesting to me because, when used with the `varFixed()` specification for the residual weights, it allows for estimation of a wide variety of meta-analysis models, including basic random effects models, bivariate models for estimating effects by trial arm, and other sorts of multivariate/multi-level random effects models.*

In contrast, @handbook2013 point out that nlme package directly gives an output for *between-studies* variance (i.e. random std. dev.) and *within-studies variance* (residuals std. dev.).

Synthesizing all of that, we fit a random-intercept model for thermal traits:

#### a) Tmin

```{r}

tmin_intercept <- lme(tmin ~ 1,
                      random = ~1|id,
                      weights = varFixed(~vi),
                      data = thetrapest,
                      control = lmeControl(sigma = 1))
summary(tmin_intercept)
VarCorr(tmin_intercept)
#performance::check_model(tmin_intercept)
```

The *summary effect* here for *T*~min~ would be an estimate of ***T***~**min**~ **= 11.12 ºC** with a *between-study* std. deviation 𝜏 **= 5.177**.

#### b) Tmax

```{r}
tmax_intercept <- lme(tmax ~ 1,
                      random = ~1|id,
                      weights = varFixed(~vi),
                      data = thetrapest,
                      control = lmeControl(sigma = 1))
summary(tmax_intercept)
VarCorr(tmax_intercept)
#performance::check_model(tmin_intercept)
```

The *summary effect* here for *T*~max~ is ***T***~**max**~ **= 11.12 ºC** with a *between-study* std. deviation **𝜏 = 6.61**.

#### c) Topt

```{r}
topt_intercept <- lme(topt ~ 1,
                      random = ~1|id,
                      weights = varFixed(~vi),
                      data = thetrapest,
                      control = lmeControl(sigma = 1))
summary(topt_intercept)
VarCorr(topt_intercept)
#performance::check_model(tmin_intercept)
```

The *summary effect* here for *T*~opt~ is ***T***~**opt**~ **= 30.37 ºC** with a *between-study* std. deviation **𝜏 = 5.075**.

#### d) a (magnitude)

```{r}
a_intercept <- lme(a_est ~ 1,
                   random = ~1|id,
                   weights = varFixed(~vi),
                   data = thetrapest,
                   control = lmeControl(sigma = 1))
summary(a_intercept)
VarCorr(a_intercept)
#performance::check_model(tmin_intercept)
```

The *summary effect* here for *a* is ***a*** **= 0.000127** with a *between-study* std. deviation **𝜏 = 0.00000104**.

#### e) Thermal breadth

```{r}
thermal_breadth_intercept <- lme(thermal_breadth ~ 1,
                                 random = ~1|id,
                                 weights = varFixed(~vi),
                                 data = thetrapest,
                                 control = lmeControl(sigma = 1))
summary(thermal_breadth_intercept)
VarCorr(thermal_breadth_intercept)
#performance::check_model(tmin_intercept)
```

The *summary effect* here for the *thermal breadth* is ***thermal breadth*** **= 15.95ºC** with a *between-study* std. deviation **𝜏 = 5.134653**.

## Incorporating covariates:

To quantify both summary effects and assess heterogeneity of the response along categorical or numerical variables, we performed hierarchical linear models (also known as *mixed-effects*) with *study* being treated again as grouping variable and variables of interest as covariates.

-   For **continuous covariates** (i.e. latitude in absolute value), we performed a *meta-regression* (as in @buckley2017 and @deutsch2008 ) with each thermal trait estimate as response variable.

For **categorical variables**, we performed hierarchical factorial models [@handbook2013] across categorical covariates such as *taxonomic order* and *feeding guild*.

#### a) Latitude

Previous studies have examined latitudinal trends of different thermal traits, either for biogeographical projections [@buckley2017; @deutsch2008] or for assessment of thermal tolerance hypotheses testing [@sunday2011; @hoffmann2013; @araújo2013].

We follow the same procedure as before incorporating absolute value of latitude to the right-hand side of the equation in the model and as numerator component of the grouping variable in the random argument.

-   *T~min~*

```{r}
# _ _ _ _ii) ~ lat  ---- 
## random slope & intercept
tmin_lat_slope <- lme(tmin ~ abs(lat),
                      random = ~abs(lat)|id,
                      weights = varFixed(~vi),
                      data = thetrapest,
                      control = lmeControl(sigma = 1))
summary(tmin_lat_slope)
```

Here, lower temperature threshold at the Equator would be **16.49 ºC** and it significantly decreases at higher latitudes, as expected (**slope = -0.175,** *p = 0.016*).

-   ***T~max~***

```{r}
# _ _ _ _ii) ~ lat  ---- 
## random slope & intercept
tmax_lat_slope <- lme(tmax ~ abs(lat),
                      random = ~abs(lat)|id,
                      weights = varFixed(~vi),
                      data = thetrapest,
                      control = lmeControl(sigma = 1))
summary(tmax_lat_slope)
```

Here, upper temperature threshold at the equator would be **35.64ºC** and it does not vary significantly along latitude (*p* = 0.797).

-   ***T~opt~***

```{r}
# _ _ _ _ii) ~ lat  ---- 
## random slope & intercept
topt_lat_slope <- lme(topt ~ abs(lat),
                      random = ~abs(lat)|id,
                      weights = varFixed(~vi),
                      data = thetrapest,
                      control = lmeControl(sigma = 1))
summary(topt_lat_slope)
```

Here, optimal temperature at the equator would be **30.60 ºC** and it does not vary significantly along latitude (*p* = 0.881).

-   ***Thermal Breadth***

```{r, }
## random slope & intercept
thermal_breadth_lat_slope <- lme(thermal_breadth ~ abs(lat),
                                 random = ~abs(lat)|id,
                                 weights = varFixed(~vi),
                                 data = thetrapest,
                                 control = lmeControl(sigma = 1))
summary(thermal_breadth_lat_slope)
```

Here, thermal breadth at the Equator would be **13.70 ºC** and it does not significantly vary across latitudes (*p* *=* 0.2).

-   ***a***

```{r}
# _ _ _ _ii) ~ lat  ---- 
## random slope & intercept
a_lat_slope <- lme(a_est ~ abs(lat),
                   random = ~abs(lat)|id,
                   weights = varFixed(~vi),
                   data = thetrapest,
                   control = lmeControl(sigma = 1))
summary(a_lat_slope) # nothing

```

Here, optimal temperature at the equator would be **30.60 ºC** and it does not vary significantly along latitude (*p* = 0.881).

#### b) Feeding guild

We subset for Borers, Chewers and Suckers feeding guilds, which are by far the most represented in the dataset.

```{r}
thetrapest_fg <- thetrapest %>% 
  filter(feeding_guild == "borer" |
           feeding_guild == "chewer" |
           feeding_guild == "sucker") 
```

-   ***T***~**min**~

```{r}
tmin_feeding_guild <- lme(tmin ~ as_factor(feeding_guild),
                          random = ~ as_factor(feeding_guild)|id,
                          weights = varFixed(~vi),
                          data = thetrapest_fg,
                          control = lmeControl(sigma = 1))
summary(tmin_feeding_guild)
emmeans(tmin_feeding_guild, list(pairwise ~ feeding_guild), adjust = "tukey")
```

Here, lower temperature thresholds are not significantly different for borers(***T***~**min**~ = **13.1ºC**), chewers (***T***~**min**~ = **10.7 ºC**) and suckers (***T***~**min**~ = **10.8 ºC**).

-   ***T***~**max**~

```{r}
tmax_feeding_guild <- lme(tmax ~ as_factor(feeding_guild),
                          random = ~ as_factor(feeding_guild)|id,
                          weights = varFixed(~vi),
                          data = thetrapest_fg,
                          control = lmeControl(sigma = 1))
summary(tmax_feeding_guild)
emmeans(tmax_feeding_guild, list(pairwise ~ feeding_guild), adjust = "tukey")
```

Here, upper temperature thresholds significantly after (Tukey's *p =* 0.0195) differ for borers (***T***~**max [borer]{.smallcaps}**~ = **32.3 ºC**) and suckers (***T***~**max [sucker]{.smallcaps}**~= **38.0 ºC**)but not for any pairwise comparison involving chewers (***T***~**max [chewer]{.smallcaps}**~ = **35.0 ºC**)

-   ***T***~**opt**~

```{r}
## random slope & intercept
topt_fg <- lme(topt ~ as_factor(feeding_guild),
                  random = ~ as_factor(feeding_guild)|id,
                  weights = varFixed(~vi),
                  data = thetrapest_fg,
                  control = lmeControl(sigma = 1))
summary(topt_fg)
emmeans(topt_fg, list(pairwise ~ feeding_guild), adjust = "tukey")
```

Here, upper temperature thresholds significantly after (Tukey's *p =* 0.0182) differ for borers (***T***~**opt [borer]{.smallcaps}**~ = **27.6 ºC**) and Acari (***T***~**opt [Acari]{.smallcaps}**~ = **31.8 ºC**)but not for any pairwise comparison involving chewer (***T***~**opt [chewer]{.smallcaps}**~= **29.4 ºC**)

-   ***T***~**Breadh**~

```{r}
## random slope & intercept
thermal_breadth_fg <- lme(thermal_breadth ~ as_factor(feeding_guild),
                          random = ~ as_factor(feeding_guild)|id,
                          weights = varFixed(~vi),
                          data = thetrapest_fg,
                          control = lmeControl(sigma = 1))
summary(thermal_breadth_fg)
emmeans(thermal_breadth_fg, list(pairwise ~ feeding_guild), adjust = "tukey")
```

Here, thermal breadth significantly differs for borers (***T***~**Breadth**~ = 12.6 **ºC**) and suckers (***T***~**Breadth**~ = **17.2ºC**) but not for any pairwise comparison involving chewer (***T***~**Breadth**~ = **15.5 ºC**).

#### c) Order

We subset for Acari, Lepidoptera and Hemiptera orders, which are by far the most represented in the dataset.

```{r}
thetrapest_order <- thetrapest %>% 
  filter(order == "Acari" |
           order == "Hemiptera" |
           order == "Lepidoptera") 
```

-   ***T***~**min**~

```{r}
## random slope & intercept
tmin_order <- lme(tmin ~ as_factor(order),
                  random = ~ as_factor(order)|id,
                  weights = varFixed(~vi),
                  data = thetrapest_order,
                  control = lmeControl(sigma = 1))
summary(tmin_order)
emmeans(tmin_order, list(pairwise ~ order), adjust = "tukey")
```

Here, lower temperature thresholds are not significantly different for Lepidoptera (***T***~**min**~ = **11.28 ºC**), Hemiptera (***T***~**min**~ = **11.87 ºC**) and Acari (***T***~**min**~ = **9.16 ºC**).

-   ***T***~**max**~

```{r}
## random slope & intercept
tmax_order <- lme(tmax ~ as_factor(order),
                  random = ~ as_factor(order)|id,
                  weights = varFixed(~vi),
                  data = thetrapest_order,
                  control = lmeControl(sigma = 1))
summary(tmax_order)
emmeans(tmax_order, list(pairwise ~ order), adjust = "tukey")
```

Here, upper temperature thresholds significantly after (Tukey's *p =* 0.0195) differ for Lepidoptera (***T***~**max [Lepidoptera]{.smallcaps}**~ = **33.3 ºC**) and Acari (***T***~**max [Acari]{.smallcaps}**~ = **40.5 ºC**)but not for any pairwise comparison involving Hemiptera (***T***~**max [hemiptera]{.smallcaps}**~ = **35.1 ºC**)

-   ***T***~**opt**~

```{r}
## random slope & intercept
topt_order <- lme(topt ~ as_factor(order),
                  random = ~ as_factor(order)|id,
                  weights = varFixed(~vi),
                  data = thetrapest_order,
                  control = lmeControl(sigma = 1))
summary(topt_order)
emmeans(topt_order, list(pairwise ~ order), adjust = "tukey")
```

Here, upper temperature thresholds significantly after (Tukey's *p =* 0.0182) differ for Lepidoptera (***T***~**opt [Lepidoptera]{.smallcaps}**~ = **33.6 ºC**) and Acari (***T***~**opt [Acari]{.smallcaps}**~ = **28.1 ºC**)but not for any pairwise comparison involving Hemiptera (***T***~**opt [hemiptera]{.smallcaps}**~ = **29.6 ºC**)

-   ***Thermal Breadth***

```{r}
## random slope & intercept
thermal_breadth_order <- lme(thermal_breadth ~ as_factor(order),
                             random = ~ as_factor(order)|id,
                             weights = varFixed(~vi),
                             data = thetrapest_order,
                             control = lmeControl(sigma = 1))
summary(thermal_breadth_order)
emmeans(thermal_breadth_order, list(pairwise ~ order), adjust = "tukey")
```

Here, thermal_breadths significantly differ for Lepidoptera (***T***~**breadh**~ = **19.4 ºC**), and Acari (***T***~**breadh**~ = **14.2 ºC**), but not for any pairwise involving Hemiptera (***T***~**breadh**~ = **15.1 ºC**).

-   ***Thermal Safety Margin (TSM)**:*

```{r}
## random slope & intercept
tsm_order <- lme(thermal_safety_margin ~ as_factor(order),
                 random = ~ as_factor(order)|id,
                 weights = varFixed(~vi),
                 data = thetrapest_order,
                 control = lmeControl(sigma = 1))
summary(tsm_order)
emmeans(tsm_order, list(pairwise ~ order), adjust = "tukey")
```

Here, the **thermal safety margin** again significantly differs for Lepidoptera (***TSM*** = **6.96 ºC**), and Acari (***TSM*** = **5.14 ºC**), but not for any pairwise involving Hemiptera (***TSM*** = **5.49 ºC**).

#### Other questions remaining: [@kingsolver; @frazier2006]

> *¿Is there a positive correlation between Topt and r? (Hotter is better)*

Esto lo podríamos estudiar con la relación entre *a* y *Topt*, ya que *a* indica la magnitud de r (mayor *a* implica mayor valor de *r*).

```{r}
topt_a <- lme(topt ~ a_est,
              random = ~1|id,
              weights = varFixed(~vi),
              data = thetrapest,
              control = lmeControl(sigma = 1))
summary(topt_a)
plot(thetrapest$topt,thetrapest$a_est)
```

> Hotter is better for mites

Los ácaros de nuestro dataset pueden servirnos para esto. Podemos ver si a mayor latitud disminuye el r, y también la propia curva para caracterizar ese *hotter is better* de forma precisa. No parece que esto se cumpla...

```{r}
thetrapest_acari <- thetrapest %>% 
  filter(order == "Acari")
a_lat_plot <- ggplot(thetrapest_acari,aes(x=abs(lat), y=a_est))+
  geom_point(color="gold2",alpha=0.1, position = position_jitter(width = 3))+
  labs(title = "Variation in magnitude of r (proxy: parameter a)",
       subtitle = "Mites",
       x = "Absolute Latitude (º)", 
       y = "a")+
  ggthemes::theme_few()+
  geom_smooth(method = "lm", color = "gold2")
a_lat_plot
```

> ¿Is there a positive correlation between Tmax and r?

Similar a la anterior, en este caso con la máxima.

> Taxa grandes aumentan Tmin más que los taxa pequeños para compensar el déficit que tienen por tamaño.

Asumiendo que lepidoptera son mucho más grandes que ácaros, cabría esperar que los ácaros varíen más sus traits hacia la derecha (ej. más respuesta a la latitud) que las mariposas, para las que el body size tiene mayor impacto relativo en el fitness. Ejemplos: la respuesta a latitud de ácaros debería ser mayor que en lepidópteros, thermal breadth de ácaros también menor que el de lepidópteros (los ácaros estarían más apretados y agobiados con desplazarse en la curva a la derecha). [Ver en apartado de thermal breadth y de latitud.]{.ul}

Según @sinclair2016, la ***thermal breadth*** la definimos como la distancia entre la temperatura en la que la respuesta es 50% del máximo por el lado izquierdo y la misma por el lado derecho; el **thermal tolerance range** es simplemente *tmax - tmin* y el **thermal safety margin** es *tmax - topt.*

## Heterogeneity of variation:

Aiming to explore biogeographical hypothesis of *cold-tolerance* [@bennett2021; @sunday2019; @sunday2011; @herrando-pérez2020], we examined how variability of estimates differs among thermal traits and across covariates such as latitude and order [@deutsch2008; @buckley2017]. Following @herrando-pérez2020 introduction, we examined variability both graphically (using boxplots, pointranges and violinplots) and tests of variance homogeneity such as Levene's).

### Graphical examination

#### Box \| Violin -- plots (traits \~ covariates)

-   **a) Order**

```{r}
boxplot_traits_ord<- ggplot(data=thetrapest_order, aes(x=order))+
  geom_boxplot(aes(y=tmin),
               fill= "turquoise4",
               color = "lightgrey")+
  geom_boxplot(aes(y=tmax),
               fill="indianred3",
               color = "lightgrey")+
  labs(title = "Thermal traits across taxa",
       x = "Order", 
       y = "Thermal traits (ºC)")+
  ggthemes::theme_few()+
  theme(axis.text.x = element_text(angle=45,vjust = 1,hjust=1))+
  theme(legend.position = "none")
boxplot_traits_ord
violin_traits_ord <- ggplot(data=thetrapest_order, aes(x=order))+
  geom_violin(aes(y=tmin),
              fill= "turquoise4",
              color = "lightgrey")+
  geom_violin(aes(y=tmax),
              fill="indianred3",
              color = "lightgrey")+
  labs(title = "Thermal traits across taxa",
       x = "Order", 
       y = "Thermal traits (ºC)")+
  ggthemes::theme_few()+
  theme(axis.text.x = element_text(angle=45,vjust = 1,hjust=1))+
  theme(legend.position = "none")
grid_hetero_tmin <- plot_grid(boxplot_traits_ord,violin_traits_ord, labels = "AUTO")
grid_hetero_tmin

```

-   **b) Feeding guild**

```{r}
boxplot_traits_fg <- ggplot(data=thetrapest_fg, aes(x=feeding_guild))+
  geom_boxplot(aes(y=tmin),
               fill= "turquoise4",
               color = "lightgrey")+
  geom_boxplot(aes(y=tmax),
               fill="indianred3",
               color = "lightgrey")+
  labs(title = "Thermal traits across feeding guilds",
       x = "Feeding guild", 
       y = "Thermal traits (ºC)")+
  ggthemes::theme_few()+
  theme(axis.text.x = element_text(angle=45,vjust = 1,hjust=1))+
  theme(legend.position = "none")
violin_traits_fg <- ggplot(data=thetrapest_fg, aes(x=feeding_guild))+
  geom_violin(aes(y=tmin),
              fill= "turquoise4",
              color = "lightgrey")+
  geom_violin(aes(y=tmax),
              fill="indianred3",
              color = "lightgrey")+
  labs(title = "Thermal traits across feeding guilds",
       x = "Feeding guild", 
       y = "Thermal traits (ºC)")+
  ggthemes::theme_few()+
  theme(axis.text.x = element_text(angle=45,vjust = 1,hjust=1))+
  theme(legend.position = "none")
plot_hetero_fg <- plot_grid(boxplot_traits_fg,violin_traits_fg)
plot_hetero_fg
```

#### Traits variability along latitude

```{r}
# ~~~~~~~~ (3) traits variability ~ lat ~----
all_lms_combined <- ggplot(thetrapest)+
  geom_point(aes(x=abs(lat),y=tmin),color="skyblue4",alpha=0.1, position = position_jitter(width = 3))+
  geom_smooth(aes(x=abs(lat),y=tmin),color="skyblue4",fill="skyblue2", method = "lm")+
  geom_point(aes(x=abs(lat),y=tmax),color="red4",alpha=0.1, position = position_jitter(width = 3))+
  geom_smooth(aes(x=abs(lat),y=tmax),color="red4",fill="red3", method = "lm")+
  geom_point(aes(x=abs(lat),y=topt),color="mediumorchid4",alpha=0.02, position = position_jitter(width = 3))+
  geom_smooth(aes(x=abs(lat),y=topt),color="mediumorchid4",fill="mediumorchid3", method = "lm", alpha = 0.01)+
  labs(title= "Thermal traits ~ latitude",x= "latitude",y= "Thermal traits (ºC)")+
  theme_few()
all_lms_combined  
breadth_order_lat <- ggplot(data = thetrapest_order, aes(abs(lat), thermal_breadth))+
  geom_point(aes(color = order), alpha =0.1)+
  facet_wrap(.~order)+
  geom_smooth(aes(color = order, fill = order), method = "lm")+
  theme_few()+
  scale_color_brewer(palette = "Set2")+
  scale_fill_brewer(palette = "Set2")+
  theme(legend.position = "none")+
  labs(x = "Absolute Latitude (º)",
       y = "Thermal Breadth (ºT)")
breadth_order_lat

```

#### traits variability \~ 1 (no covariate)

```{r}
violin_traits_all <- ggplot(data=thetrapest,aes(x=1))+
  geom_violin(aes(y=tmin),
              fill= "turquoise4",
              color = "lightgrey")+
  geom_violin(aes(y=tmax),
              fill="indianred3",
              color = "lightgrey")+
  labs(title = "Thermal traits across taxa",
       x = element_blank(),
       y = "Thermal traits (ºC)")+
  ggthemes::theme_few()+
  theme(axis.text.x = element_blank())+
  theme(legend.position = "none")
violin_traits_all

```

### Quantitative Analysis of heterogeneity

We aim to evaluate whether lower and upper thermal traits' variabilities differ. First we perform a F-test, similarly to @herrando-pérez2020

```{r}
# ~~~~~~~~  (1) F-test (see Herrando-Pérez, 2019) ----
variances_tmin <- thetrapest %>% 
  select(tmin, vi, id) %>% 
  mutate(parameter = rep("tmin")) %>% 
  rename(estimate = tmin)
variances_tmax <- thetrapest %>% 
  select(tmax, vi, id) %>% 
  mutate(parameter = rep("tmax")) %>% 
  rename(estimate = tmax)
variances_traits = variances_tmin %>% 
  bind_rows(variances_tmax)
#test variance differences
var.test(estimate ~ parameter, variances_traits, 
         alternative = "greater") #que tmin tiene más varianza que tmax

```

We confirm that variance of lower temperature threshold is higher than upper temperature threshold (F = 1.5791; *p* \< 0.001).

Now we perform a Levene test of variance homogeneity as in @hoffmann2013, which confirm the previous result (F = 5.224, *p* = 0.0223).

```{r}
# ~~~~~~~~  (2) Levene's test (see Hoffmann, 2013) ----
leveneTest(y = estimate ~ parameter, data = variances_traits) # also 

```

Next, we use the meta-analysis *true* between-studies heterogeneity (i.e. 𝜏). In this case, we standardise the value by dividing the 𝜏 by the estimate.

```{r}
# ~~~~~~~~ (3) lme modelling output ----
lme_4vars <- lme(tmin ~ 1,
                 random = ~1|id,
                 weights = varFixed(~vi),
                 control = lmeControl(sigma = 1),
                 data = thetrapest)
lme_4vars2 <- lme(tmax ~ 1,
                 random = ~1|id,
                 weights = varFixed(~vi),
                 control = lmeControl(sigma = 1),
                 data = thetrapest)


tau_rel_tmin <- as.numeric(VarCorr(lme_4vars)[1,2])/lme_4vars$coefficients$fixed
tau_rel_tmax <- as.numeric(VarCorr(lme_4vars2)[1,2])/lme_4vars2$coefficients$fixed
# similar...
```

And it confirms again that the effect sizes variability is higher for *T*~min~ than for *T*~max.~

# References
